---
title: 'Unit 12 HW: The Classical Linear Model, Question 1.5'
author: "Abraham Yang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r load packages, include=FALSE}
library(tidyverse)
library(patchwork)
library(car)
library(lmtest)
library(sandwich)
library(stargazer)
library(gridExtra)
library(lattice)
library(dplyr)
install.packages("dgof")
library("dgof")
install.packages('tseries')
library(tseries)
```

```{r chunk options, include=FALSE}
knitr::opts_chunk$set(message=FALSE, dpi=300)
```

```{r load-data, message=FALSE, include=FALSE}
videos <- read_delim("videos.txt", delim = "\t")
videosfo <- videos %>% filter(!is.na(videos$views))
videosclean <- videosfo[videosfo$rate>=1,]
videosclean <- videosclean[videosclean$length<=660,]
glimpse(videosfo)
summary(videosclean)
```

```{r, include=FALSE}
videos_model <-lm(log(views) ~ rate + length, data=videosfo)
videos_model_clean <-lm(log(views) ~ rate + length, data=videosclean)
```

```{r include=FALSE}}
vids_resids = resid(videos_model_clean)

```

```{r out.width="70%", align = 'center', fig.cap="Residuals vs. Normality", echo=FALSE, include=TRUE}

plot_one <- videosclean %>%
  ggplot(aes(x = vids_resids)) +
  geom_histogram()

plot_two <- videosclean %>%
  ggplot(aes(sample = vids_resids)) +
  stat_qq() + stat_qq_line()

plot_one / plot_two
```
The histogram of residuals and the qqplot show a normal distribution, albeit imperfect. 

```{r Kolmogorov-Smirnov Test, include=TRUE}
ks.test(vids_resids, "pnorm")
```
```{r Shapiro–Wilk Test, include=TRUE}}
shapiro.test(sample(vids_resids, size = 5000, replace = TRUE))
```

```{r Jarque Bera Test, include=TRUE}
jarque.bera.test(sample(vids_resids, size = 5000, replace = TRUE))
```
Looking at the p-values from the Kolmogorov-Smirnov test, Shapiro–Wilk test, and Jarque Bera test, all the p-values are less than 0.05, therefore we reject the null hypotheses that the residual distribution comes from a normal distribution. However, in large samples such as this dataset, CLT kicks in. And the more we add datapoints, the more the CLM tests will fail.