---
title: "Estimating Coffee Ratings - Dataset from Coffee Quality Institute"
author: "Abraham Yang, Erica Nakabayashi, Melissa Oliveira"
date: '2023-03-30'
output: pdf_document
header-includes:
 \usepackage{wrapfig}
 \usepackage{float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages and set options, include=FALSE}

library(tidyverse)
library(magrittr)
library(stargazer)
library(sandwich)
library(lmtest)

theme_set(theme_bw())

```

```{r load data, message = FALSE, include=FALSE}

original_coffee <- read.csv("merged_data_cleaned.csv")

```

```{r data summary}

summary(original_coffee)

```

```{r oh no duplicates}
metad_coffee <- original_coffee[original_coffee$Owner=="metad plc" & original_coffee$Farm.Name=="metad plc",]
head(metad_coffee)
```

```{r filtering out mash up}
coffee<-unique(original_coffee[,c("Species", "Owner", "Owner.1", "Farm.Name", "Producer", "Harvest.Year", "Expiration")])
```


```{r data glimpse}
nrow(coffee)
```
original_coffee[,c("Lot.Number", "ICO.Number", "Country.of.Origin","Category.One.Defects","Category.Two.Defects","Total.Cup.Points","altitude_low_meters")]

```{r variable add columns}
sum(original_coffee=="")
```

```{r data head}
which(original_coffee=="", arr.ind=TRUE)
```


Since there's is more than a few duplicate values, we will be assuming average rates for the values that have more than one entry. That might happen because, CQI has 3 different trained evaluators test out the coffee according to their evaluation process documentation (<https://database.coffeeinstitute.org/api/s3proxy/get/coffee/files/f05qp1bqg3/Process%20for%20Evaluating%20Coffees%20in%20the%20Q%20Coffee%20System%20March%202022.pdf>).

```{r tbc}



```
